Efficiently Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-13 tab-desth.tex
tex

\begin{table}
\resizebox{\columnwidth}{!}{
\begin{tabular}{c|cc|cc|cc|cc|cc}

	\toprule

@@

Random & \uline{53.9} & \uline{3.8} & 27.4 & 32.9 & \multicolumn{2}{c|}{Collapse} & \multicolumn{2}{c|}{Collapse} & \multicolumn{2}{c|}{Collapse}\tabularnewline
\hline 
Semihard & 46.9 & 4.1 & - & - & \multicolumn{2}{c|}{Collapse} & \multicolumn{2}{c|}{Collapse} & \multicolumn{2}{c|}{Collapse}\tabularnewline
\hline 
Softhard &  &  &  &  & - & - & \multicolumn{2}{c|}{Collapse} & \multicolumn{2}{c|}{Collapse}\tabularnewline
\hline 
Distance &  &  &  &  &  &  & - & - & 52.1 & 4.7\tabularnewline
\hline 
Hardest &  &  &  &  &  &  &  &  & \uline{48.9} & \uline{5.0}\tabularnewline

@@

\caption{Hardness Manipulation: Source hardness v.s. Destination hardness for
amdsemi on CUB Dataset. (R@1, ERS for each cell). Diagonal = does
not attack}
\label{tab:desth}

>>>>

\begin{table}
\resizebox{\columnwidth}{!}{
\setlength{\tabcolsep}{0.3em}
\begin{tabular}{c|cc|cc|cc|cc|cc}
	\toprule

@@

Random & \cellcolor{black!10} 53.9 & \cellcolor{black!10}3.8 & 27.0 & 35.1 & \multicolumn{2}{c|}{Collapse} & \multicolumn{2}{c|}{Collapse} & \multicolumn{2}{c|}{Collapse}\tabularnewline
\hline
Semihard & 43.9 & 5.4 & \cellcolor{black!10}44.0 & \cellcolor{black!10}5.0 & \multicolumn{2}{c|}{Collapse} & \multicolumn{2}{c|}{Collapse} & \multicolumn{2}{c|}{Collapse}\tabularnewline
\hline
Softhard & 48.3 & 13.7 & 38.4 & 29.6 & \cellcolor{black!10}55.7 & \cellcolor{black!10}6.2 & \multicolumn{2}{c|}{Collapse} & \multicolumn{2}{c|}{Collapse}\tabularnewline
\hline
Distance & 52.7 & 4.8 & 50.7 & 4.8 & \multicolumn{2}{c|}{Collapse} & \cellcolor{black!10}51.4 & \cellcolor{black!10}4.9 & 54.7 & 5.4\tabularnewline
\hline
Hardest & 51.0 & 4.7 & 52.2 & 4.8 & \multicolumn{2}{c|}{Collapse} & 52.6 & 5.1 & \cellcolor{black!10}48.9 & \cellcolor{black!10}5.0\tabularnewline

@@

\caption{Combinations of Source/Destination Hardness.
	%
	Experiments are conducted on CUB Dataset.
	%
	Models on the diagonal do not use adversarial examples
	due to destination being unchanged.
	%
}
\label{tab:desth}
